Approximate State Abstraction

### 2016-01-29 paper/paper.tex
Trying to pull

Note that as $t \rightarrow \infty$, $\sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} \rightarrow \frac{2\epsilon}{(1-\gamma)^2}$ by the sum of a geometric series and $\pi_{A,t}(s) \rightarrow \pi_A^*(\epQ(s))$.

>>>>

Note that as $t \rightarrow \infty$, $\sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} \rightarrow \frac{2\epsilon}{(1-\gamma)^2}$ by the sum of geometric series and $\pi_{A,t}(s) \rightarrow \pi_A^*(\epQ(s))$.
